---
title: "p8105_hw1_mb5357"
author: "Maria Beg"
date: "2025-09-18"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(moderndive)

```

## Loading the dataset

```{r}

data("early_january_weather")

```

## Decription of the dataset

Used View() to look at the dataset. 

There are 15 variables in this dataset.

Variables in the dataset are `origin`, `year`, `month`, `day`, `hour`, `temp`, `dewp`, `humid`, `wind_dir`, `wind_speed`, `wind_gust`, `precip`, `pressure`, `visib`, and `time_hour`.

The important variables:

`temp` = The temperature in Fahrenheit

`humid` = The relative humidity

`time_hour` = Date and Hour when each observation was recorded


## Size of the dataset

```{r}

num_rows <- nrow(early_january_weather)

num_cols <- ncol(early_january_weather)

mean_temp <- mean(pull(early_january_weather, temp))

```

The number of rows is `r num_rows` and the number of columns is `r num_cols` in the dataset.

The mean temp is `r round(mean_temp, 2)`.



