---
title: "p8105_hw1_mb5357"
author: "Maria Beg"
date: "2025-09-18"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(moderndive)

```

## PROBLEM 1


## Loading the dataset

```{r}

data("early_january_weather")

```

## Decription of the variables

Used View() to look at the dataset. 

There are 15 variables in this dataset.

Variables in the dataset are `origin`, `year`, `month`, `day`, `hour`, `temp`, `dewp`, `humid`, `wind_dir`, `wind_speed`, `wind_gust`, `precip`, `pressure`, `visib`, and `time_hour`.

The important variables:

`temp` = The temperature in Fahrenheit

`humid` = The relative humidity

`time_hour` = Date and Hour when each observation was recorded


## Size of the dataset

```{r}

num_rows <- nrow(early_january_weather)

num_cols <- ncol(early_january_weather)

```

The number of rows is `r num_rows` and the number of columns is `r num_cols` in the dataset.


## The mean temperature 

```{r}

mean_temp <- mean(pull(early_january_weather, temp))

```

The mean temp is `r round(mean_temp, 2)`.


## Scatterplot of `temp` v/s `time_hour`

```{r}

ggplot(early_january_weather, 
       aes(x = time_hour, 
           y = temp, 
          color = humid)) +
          geom_point() +
  labs(
    title = "Temperature vs Time in Early January",
    x = "Time (hour)",
    y = "Temperature (F)",
    color = "Humidity"
  )


```

The scatterplot shows that temperature fluctuates over time, likely reflecting daily cycles. Humidity values appear to increase around mid-January, suggesting a shift in weather conditions during that period.

## Saving the scatterplot

```{r}

ggsave("p1805_hw1_mb5357_scatterplot.pdf")

```


## PROBLEM 2


## Creating a dataframe

```{r}

samp <- rnorm(10)

sample_df = tibble(
  sample = samp,
  sample_greater_than_0 = sample > 0,
  chr_vec =  rep(c("red", "blue","yellow", "green", "purple"), length.out = 10),
  fac_vec = factor(rep(c("A", "B", "C"), length.out = 10))
)

```


## Taking the mean of each Variable

```{r}

mean_num <- mean(pull(sample_df, sample))

mean_greater_than_0 <- mean(pull(sample_df, sample_greater_than_0))

mean_char <- mean(pull(sample_df, chr_vec))

mean_fac <- mean(pull(sample_df, fac_vec))

```

The mean works for the numeric vector and the logical vector. However, the mean fails for the character and factor vectors, producing a warning message and returning NA.




